---
title: "vignette-G5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette-G5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ProjectG5)
```

### Welcome to our project about anime !

The Shiny App we have created for this project concerns an anime recommendation based on these parameters:
- age of the person
- preferred anime genre (action, fantasy, etc.)
- time available to watch the anime

These different parameters will give a recommendation of an anime name.

### Example of how to use the application

Let's take the example of a 15 years old person, who likes fantasy and comedy anime and has 30 minutes to watch an episode. This person will first write his/her age, then the two genres he/she likes (Comedy, Fantasy) thanks to the drop-down menu offered by the application. Then, she will take the cursor and indicate "30" in the time available per minutes.

We will then notice that Naruto will appear first as a recommendation. This seems plausible, since Naruto is an anime mainly aimed at children and teenagers. Moreover, each episode of Naturo lasts between 20 and 30 minutes.
